Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-25 ECCV/paper.tex
Added other fiducial images

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers \
\pagestyle{headings}
\mainmatter
\def\ECCV14SubNumber{150}  % Insert your submission number here

@@

\section{Related Work}
The ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} is well known toolkit in
Augmented Reality system, widely used to find pose of the object on which it is
placed.  Fiala et al. \cite{Fiala05} developed fiducial named, ARTag, bi-tonal
system containing 2002 planar markers, each consisting of a square border and
an interior region filled with a 6x6 grid of black or white cells. It proved to
be more efficient than \cite{ARToolkit02} in terms of marker recognition rate
as well as the number of different patterns which can be created.

Concentric Rings are reported used first by Gatrell et al.\cite{concentric} for
monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings in wide area
tracking in large scale applications. In \cite{NaimarkF02}, Naimark et al.
have developed ``Circular Data Matrix Fiducial System'', for wide area tracking.

@@

Bergamasco et al. \cite{runetag11} developed RUNE-Tag, fiducial marker
system which works under large amount of occlusion. Bergamasco et al. also 
designed Pi-Tag \cite{Pitag13}, marker design based on projective
invariants.
Wu et al.\cite{Wu:2011} have developed BLUr-driven Tracker (BLUT) framework for
tracking motion-blurred targets.

\section{Design of Fiducial}
Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
that may be thought of as a binary code.  It contains concentric white rings of
equal widths on a black background with a blurred border. The outermost and
innermost rings represent the start and end of the code and is embedded in the
fiducial; these are not considered part of the code itself. The binary code is
represented by the presence (or absence) of rings between ``marker'' rings.
Depending on which ring is present or absent, the resulting binary code will
change. The number of different patterns depends on the number of bits in the
binary code. For example, if the binary code has three bits, there will be a
maximum of three rings between``marker'' rings and we end up with eight
different patterns.

@@

\begin{figure}
\centering
  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_180.jpg}  
  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_45.jpg}
  \includegraphics[width=.3\linewidth]{concentric_01_5_blurred_90.jpg}  
  \caption{Sample images used to create training data for the fiducial pattern
  with binary code ``01''}
\end{figure}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers \

\pagestyle{headings}
\mainmatter
\def\ECCV14SubNumber{150}  % Insert your submission number here

@@

\section{Related Work}

\begin{figure}

 \begin{subfigure}[b]{0.19\textwidth}  
 \centering 
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  \caption{ARToolkit}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  \caption{ARTag}
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  \caption{Intersense}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.png}
  \caption{Pi-Tag}  
 \end{subfigure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{newconcentric_01.pdf}
  %\includegraphics[width=0.5\linewidth]{newconcentric_10.pdf}
  \caption{Our Fiducial}  
 \end{subfigure}
 \caption{Various Fiducial Marker Designs}
 \label{fig:previous_work}  
\end{figure}

The ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} is well known toolkit in
Augmented Reality system, widely used to find pose of the object on which it is
placed.  Fiala et al. \cite{Fiala05} developed fiducial named, ARTag, bi-tonal
system containing 2002 planar markers, each consisting of a square border and
an interior region filled with a 6x6 grid of black or white cells. It proved to
be more efficient than \cite{ARToolkit02} in terms of marker recognition rate
as well as the number of different patterns which can be created.

Concentric Rings are reportedly used first by Gatrell et al.\cite{concentric}
for monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings in wide area
tracking in large scale applications. In \cite{NaimarkF02}, Naimark et al.
have developed ``Circular Data Matrix Fiducial System'', for wide area tracking.

@@

Bergamasco et al. \cite{runetag11} developed RUNE-Tag, fiducial marker
system which works under large amount of occlusion. Bergamasco et al. also 
designed Pi-Tag \cite{Pitag13}, marker design based on projective
invariants.

\subsection{Limitations}
The main hurdle in detection of current fiducials is, the detecton of features;
lines in \cite{ARToolkit02}, corners in \cite{Fiala05} while ellipses in
\cite{Cho:2001}, \cite{Cho97fastcolor}, \cite{runetag11} and \cite{Pitag13}.
Such features are very difficult to correctly detect under significant motion
blur. So, under blur, recognition rate of these fiducials is very low.

Wu et al.\cite{Wu:2011} have developed BLUr-driven Tracker (BLUT) framework for
tracking motion-blurred targets. BLUT framework works well when there is
uniform motion and the position of tracked object does not change drastically in
successive frames. But in our case, due to frequntly dropping of intermediate
frame, this criterion may not be satisfied.

\section{Design of Fiducial}
Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
that may be thought of as a binary code.  It contains concentric white rings of
equal widths on a black background with a blurred border. The outermost and
innermost rings represent the start and end of the code and is embedded in the
fiducial; these are not considered part of the code itself. The binary code is
represented by the presence (or absence) of rings between ``marker'' rings.

Depending on which ring is present or absent, the resulting binary code will
change. The number of different patterns depends on the number of bits in the
binary code. For example, if the binary code has three bits, there will be a
maximum of three rings between``marker'' rings and we end up with eight
different patterns. Fig. \ref{fig:fiducials} shows two bit binary coded
fiducials.

@@

\begin{figure}
\centering
  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_180.jpg}  
  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_45.jpg}
  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_90.jpg}  
  \includegraphics[width=.22\linewidth]{concentric_01_5_blurred_135.jpg}
  \caption{Sample images used to create training data for the fiducial pattern
  with binary code ``01''}
\end{figure}
